The promise of community-driven preprints in ecology and evolution

### 2024-10-14 ms/ms.qmd
added in lack of discussion point
C38 & C41

- Third, seek out and contribute to constructive feedback on preprints [@bourne2017ten]. While it is clear that preprints help establish precedence and allow findings to be openly accessible, it still seems rare that constructive discussions form around preprints in an open forum (e.g. *bioRxiv* [@anderson2020biorxiv]).  Unfortunately, the *EcoEvoRxiv* website does not provide opportunities for discussion given the limitations of the web server at this point in time. As such, we could not accurately assess how much discourse around a given preprint occurs. One way to facilitate such discussions may be to use open preprint peer-review services such as *Peer Community In* (PCI) or *PubPeer* (see also [@avissar2024recommendations]) to provide feedback on preprints. Both *PCI* and *PubPeer* provide opportunities for open peer review around a preprint that are given a unique DOI which can then be associated with a preprint on *EcoEvoRxiv*. However, *EcoEvoRxiv* currently lacks connection to *PCI*, *PubPeer* and Altmetric data which would allow for discussion to be assimilated around a preprint in one place and make it easy for readers to see discourse around a preprint. Clearly, as a community, we need to provide better platforms and workflows that document discussions around preprint findings. Such discussions help authors improve their work and communicate their findings more effectively (when done constructively, of course). An important future goal of *EcoEvoRxiv* is to provide better community discussion forums and integration with existing preprint peer review services. 

>>>>

- Third, seek out and contribute to constructive feedback on preprints [@bourne2017ten]. While it is clear that preprints help establish precedence and allow findings to be openly accessible, it still seems rare that constructive discussions form around preprints in an open forum (e.g. *bioRxiv* [@anderson2020biorxiv]).  Unfortunately, the *EcoEvoRxiv* website does not provide opportunities for discussion given the limitations of the web server at this point in time. As such, we could not accurately assess how much discourse around a given preprint occurs. One way to facilitate such discussions may be to use open preprint peer-review services such as *Peer Community In* (PCI) or *PubPeer* (see also [@avissar2024recommendations]) to provide feedback on preprints. Both *PCI* and *PubPeer* provide opportunities for open peer review around a preprint that are given a unique DOI which can then be associated with a preprint on *EcoEvoRxiv*. However, *EcoEvoRxiv* currently lacks connection to *PCI*, *PubPeer* and Altmetric data which would allow for discussion to be assimilated around a preprint in one place and make it easy for readers to see discourse around a preprint. Clearly, as a community, we need to provide better platforms and workflows that document discussions around preprint findings. Such discussions help authors improve their work and communicate their findings more effectively (when done constructively, of course). Lack of discussion around preprints more generally might also be a function of time constraints researchers face and the lack of credit received for such a community service. An important future goal of EcoEvoRxiv is to provide better community discussion forums and integration with existing preprint peer review services. We also need to find new ways to give credit to colleagues that contribute to community discussion. 
